Approximation as Differentiation notes

### 2025-02-27 notes/sec/grothendieck.tex
Less general prop 2.12.

\begin{proposition}
Suppose $C$ locally small.
\begin{enumerate}
\item If $C$ has binary coproducts and set-indexed products, then $\Fam(C)$ is symmetric monoidal, with the
coproduct as the monoidal product.
\item If the coproducts are in fact biproducts, then $\Fam(C)$ is Cartesian closed.
\end{enumerate}
\end{proposition}

\begin{proof}
Suppose $C$ locally small with binary biproducts given by $(\biprod,\inj,\proj)$ and set-indexed products
given by $(\prod,\eval_{\prod},\lambda_{\prod})$. For any objects $X = (I, X), Y = (J, Y)$ and $Z = (K, Z)$ in
$\Fam(C)$ define:

>>>>

\begin{proposition}
Suppose $C$ locally small. If $C$ has binary biproducts and set-indexed products, then $\Fam(C)$ is Cartesian
closed. \todo{Establish first that if $C$ has binary coproducts and set-indexed products, then $\Fam(C)$ is
symmetric monoidal, with the coproduct as the monoidal product.}
\end{proposition}

\begin{proof}
Suppose $C$ is locally small, with binary biproducts given by $(\biprod,\inj,\proj)$ and set-indexed products
given by $(\prod,\eval_{\prod},\lambda_{\prod})$. For any objects $X = (I, X), Y = (J, Y)$ and $Z = (K, Z)$ in
$\Fam(C)$ define:
